---
title: "Exploring Gun Deaths in America"
author: "Your name"
output: github_document
---

## Get the data

```{r}
# don't modify this chunk unless you still need to install rcfss
# if so, run "devtools::install_github("uc-cfss/rcfss")" in the console first

library(tidyverse)    # load tidyverse packages, including ggplot2
library(rcfss)

# load the data
data("gun_deaths")
gun_deaths
```

## In what month do the most gun deaths occur?

```{r}

```

## What is the most common intent in gun deaths? Do most people killed by guns die in suicides, homicides, or accidental shootings?

```{r}

```

## What is the average age of females killed by guns?

```{r}

```

## How many white males with at least a high school education were killed by guns in 2012?

```{r}

```

## Which season of the year has the most gun deaths?

Assume that:

* Winter = January-March
* Spring = April-June
* Summer = July-September
* Fall = October-December

```{r}

```

# What is the relationship between race and intent?

For example, are whites who are killed by guns more likely to die because of suicide or homicide? How does this compare to blacks and hispanics?

```{r}

```

# Are police-involved gun deaths significantly different from other gun deaths? Assess the relationship between police involvement and age, police involvement and race, and the intersection of all three variables.

```{r}

```

## Session info

```{r}
# don't modify this chunk
devtools::session_info()
```


