---
title: "Exploring U.S. Supreme Court Decisions"
author: "Your name"
output: github_document
---

## Get the data

```{r, echo = TRUE}
# load useful packages
library(tidyverse)

# load data
scdbv_mod <- read_csv("data/SCDB_2017_01_justiceCentered_Citation.csv")
scdbv_leg <- read_csv("data/SCDB_Legacy_03_justiceCentered_Citation.csv")
scdbv_mod
scdbv_leg
```

## Combine the datasets

```{r}
# scdbv <- # add your code here
```

## Recode variables as you find necessary

```{r}

```

## What percentage of cases in each term are decided by a one-vote margin (i.e. 5-4, 4-3, etc.)

```{r}

```

## In each term he served on the Court, in what percentage of cases was Justice Antonin Scalia in the majority?

```{r}

```

## Create a graph similar to above that compares the percentage for all cases versus non-unanimous cases (i.e. there was at least one dissenting vote)

```{r}

```

## In each term, what percentage of cases were decided in the conservative direction?

```{r}

```

## The Chief Justice is frequently seen as capable of influencing the ideological direction of the Court. Create a graph similar to the one above that also incorporates information on who was the Chief Justice during the term.

```{r}

```

## Session info

```{r, echo = TRUE}
devtools::session_info()
```


